LAGOS lake depth

### 2020-01-08 figures/01_contrasts.Rmd
add glaciation contrast

```{r 01_contrasts_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 4}
cowplot::plot_grid(gg_depth_shape_class + 
                     theme(axis.text.x = element_text(angle = 90)), 
                   gg_depth_conny_class + 
                     theme(# axis.text.y = element_blank(), 
                           axis.title.y = element_blank(), 
                           axis.text.x = element_text(angle = 90)))
```

>>>>

```{r gg_depth_glaciated, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

gg_depth_glaciated_class <- dt %>%
  dplyr::filter(!is.na(lake_glaciatedlatewisc)) %>%
  group_by(lake_glaciatedlatewisc) %>%
  summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = lake_glaciatedlatewisc, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")
```

```{r 01_contrasts_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height = 3.5}
theme_opts <- theme(axis.text.x = element_text(angle = 90))

cowplot::plot_grid(gg_depth_shape_class + 
                     theme_opts, 
                   gg_depth_conny_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   gg_depth_glaciated_class + 
                     theme_opts +
                     theme(axis.title.y = element_blank()), 
                   nrow = 1)
```
